\large Fowizzle: Combining spectra or images by forward modeling

### 2024-03-15 paper/main.tex
tiny

\paragraph{Flux or photon conservation}
Some methods for image combination, like \texttt{Drizzle}, have as a hard constraint that they conserve \emph{flux} or \emph{photons}.
We do not agree with this constraint or condition.
The fundamental observable in a telescope is intensity, or energy per area per time per wavelength (or per frequency).
This quantity is related to the phase-space density of photons.
When the pixel grid of an imager is changed, the expectation of the rate of photon arrivals per pixel will change, but the expectation of the intensity will not change.
Our position is that the key idea is not the conservation of flux or photons, but that the spectra or images being combined make the same measurements of the intensity (or similarly normalized measurements of intensity) at the detector surface.
The combined or average image should be the provide the best estimate of this (possibly normalized) intensity.

>>>>

\paragraph{Flux or photon conservation}
Some methods for image combination, like \texttt{Drizzle} \citep{drizzle}, have as a hard constraint that they conserve \emph{flux} or \emph{photons}.
We do not agree with this constraint or condition.
The fundamental observable in a telescope is intensity, or energy per area per time per wavelength (or per frequency).
This quantity is related to the phase-space density of photons.
When the pixel grid of an imager is changed, the expectation of the rate of photon arrivals per pixel will change, but the expectation of the intensity will not change.
Our position is that the key idea is not the conservation of flux or photons, but that the spectra or images being combined make the same measurements of the intensity (or similarly normalized or otherwise consistently calibrated measurements of intensity) at the detector surface.
The combined or average image should be the provide the best estimate of this intensity.
